---
title: "riddlerontheroof"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{riddlerontheroof}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package serves as a distraction for anyone experiencing pain or sadness from coding.
It will randomly generate riddles from a preloaded list of riddles (included in package).
Riddles from https://github.com/crawsome/PyRPG_Mini.git

There are 4 functions included in this package:
1) getRiddles
2) riddlemethis
3) addriddles
4) howmanyRiddles

Below, I will go over what each function does (it's quite simple).

Load the package:
```{r setup}
library(riddlerontheroof)
```

To load riddles:
**Make sure to always load riddles onto object 'riddles'**
```{r}
riddles <- getRiddles()
```

To play riddlerontheroof:
```{r}
riddlemethis(riddles)

# What measures out time. Until in time all is smashed to it? 
# Your answer ('Q' to exit): 
# WRONG. The correct answer was:  Sand 
# Ten men's strength, ten men's length. Ten men can't break it, yet a young boy walks off with it. 
# Your answer ('Q' to exit): rope
# Good job!
# A tiny bead, like fragile glass, strung along a cord of grass. 
# Your answer ('Q' to exit): Q
# Quitting the game. Score:  1 
# NULL
```

To add your own riddles:
```{r}
addRiddles("What has to be broken before you use it?", "egg")
```

To see how many riddles you have:
```{r}
howmanyRiddles(riddles)
```

Thanks!